\plaintitle

### 2018-04-03 paper/paper.tex
...

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{``\texttt{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  When a user wants to ``make the room darker'',
  he should translate it to a real action like ``turn off the ceiling light''.
  To do so,
  he may have to ``toggle the wall switch''
  or issue a command like ``\texttt{\$ iot ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his intention
  ``使房黒暗'' into ``make the room darker'',
  translate it to ``turn off the ceiling light'', 
  and finally generate a command string like ``\texttt{\$ iot ceilinglight 0}''.

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \texttt{git} commands
  from fragments of users' intentions.

@@

For example, the database can include data like
\texttt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \texttt{git} command
using the {\EH} framework.

@@

We assume that the user is using \texttt{bash} for his software
development activities.

@@

When the user wants to compare the latest \texttt{README.md} file with an
older version, he tries to use \texttt{git} to show the difference.
He may know that he can use the \texttt{git diff} command to do the
conparison and invoke the following command like the following.

@@

Nothing happens, because this is not the approriate command
to compare the latest version of \texttt{README.md}
with older versions.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
specifies a file included in the older ``commit'',
and the following command only compares the \texttt{README.md}
with the with the file included in the last commit, where
\texttt{README.md} might be the same as the latest version.

@@

If {\GH} is installed,
the user can type a special key (e.g. \texttt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\verb|git RE |'' to see how he can do the job.

@@

A description like ``1日前''(1 day ago) was also shown in the candidate list.
This means that the user can use the same string ``\texttt{git RE 1}''
for getting the README.md file of the day before yesterday.
The command is ``\verb|$ git ... '@{1 days ago}|''.
Although such command options are very difficult to remember,
users can do the same thing only by saying \texttt{RE} and \texttt{1}.

@@

{\EH} implementation

\subsection{Translation}

A powerful text-search mechanism called {\EH} is used in the
background of {\GH}.

{\EH} systemm is used in {\GH}.

@@

Approximate pattern matching

@@

The translation data of {\GH} is written on {\SB} pages on the Web.
{\SB} is a general-purpose flexible and powerful Wiki system where
users can put any kind of data for sharing.
For {\GH}, database entries like the following

(Figure)

Specs and command lines are specified with a special symbol, and
all other documents can be written just like standard manuals and help documents.

The document and the specs are written in the same document

This is
``literate programming'' style where
source codes and documents are put in the same place.

@@

On text editors an│shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \tt{la} on the Unix shell,
\tt{latex}, \tt{latex}, and other commands are shown as candidates.
When a user types \tt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \texttt{README.md} file, and
replace the user's input with \tt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been adopted in text editors and command line editors.

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \texttt{git} users by dynamically
showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

>>>>

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\sf#1{\textsf{#1}}
\long\def\qtt#1{``\texttt{#1}''}
\long\def\qsf#1{``\textsf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  When a user wants to ``make the room darker'',
  he should translate it to a real action like ``turn off the ceiling light''.
  To do so,
  he may have to ``toggle the wall switch''
  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his intention
  ``使房黒暗'' into ``make the room darker'',
  translate it to ``turn off the ceiling light'', 
  and finally generate a command string like ``\tt{\$ iot ceilinglight 0}''.

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.

@@

For example, the database can include data like
\tt{\[ heya wo kuraku suru, \% iot ceiling 0 \]}.

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

We assume that the user is using \tt{bash} for his software
development activities.

@@

When the user wants to compare the latest \tt{README.md} file with an
older version, he tries to use \tt{git} to show the difference.
He may know that he can use the \tt{git diff} command to do the
conparison and invoke the following command like the following.

@@

Nothing happens, because this is not the approriate command
to compare the latest version of \tt{README.md}
with older versions.
%
More experienced user might use a command like the following,
but it does not show anything either, because the version specification
``\verb|HEAD^^|''
specifies a file included in the older ``commit'',
and the following command only compares the \tt{README.md}
with the with the file included in the last commit, where
\tt{README.md} might be the same as the latest version.

@@

If {\GH} is installed,
the user can type a special key (e.g. \tt{Cmd-Ctrl-G}) to invoke {\GH}
after typing ``\verb|git RE |'' to see how he can do the job.

@@

A description like ``1日前''(1 day ago) was also shown in the candidate list.
This means that the user can use the same string ``\tt{git RE 1}''
for getting the README.md file of the day before yesterday.
The command is ``\verb|$ git ... '@{1 days ago}|''.
Although such command options are very difficult to remember,
users can do the same thing only by saying \tt{RE} and \tt{1}.

@@

{\EH} search algorithm and database structure

% \subsection{Translation}

A powerful information retrieval mechanism called {\EH} is used in {\GH}.

Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression which represents the help entry description
and a corresponding command pattern.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands or calling library functions
corresponding to the description.
%
For example, a help entry for finding a restaurant on the Web consists of
the following data:

\begin{quote}
  description: \\
  \tt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
  command: \\
  \tt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
\end{quote}

The first regular expression, the description part,
is for generating texts like
\qsf{Find a Chinese restaurant in San Francisco}, 
\qsf{Find a Chinese restaurant in Chicago}, etc.,
and the second part, command part,
is used to generate a command for accessing \tt{Yelp.com}.
In the first example, \qsf{Chinese} and \qsf{San Francisco}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a URL
\tt{http://www.yelp.com/search?find\_loc=San\%20Francisco\&find\_desc=Chinese}.

When the matched pattern like \qsf{San Francisco}
cannot be directly used in the command,
parameters for the command can be put after the description string,
separated by a TAB character.
For example, when a number like ``\tt{29247}'' should be used
for checking the
weather of San Francisco, we can describe the help entry like this:

\begin{quote}\small
 description: \\
 \tt{Check the weather of (San Francisco{\textbackslash}t29247| New York{\textbackslash}t23164)} \\
 command: \\
 \tt{open 'http://local.msn.com/ten-day.aspx?\\eid=\$1'}
\end{quote}

Here, selecting a menu entry \qsf{Check the weather of San Francisco}
will produce a command
\tt{open 'http:{\slash}{\slash}local. msn.com{\slash}ten-day.aspx?eid=29247'}.

\subsection{(section written for GitHelp)}

@@

\subsection{Generating help menu entries}

Finding appropriate entries from the huge help document space is performed in two steps.
First, we parse the regular expression to
generate a state transition diagram that represents all the strings represented
in the regular expression.
Second, we generate all the description strings by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

\subsubsection{Phase 1: Generating a state transition diagram from a regular expression}

Regular expressions are widely used for finding patterns in text strings
in modern programming languages and in the Unix environment.
In {\EH}, we use regular expressions for
generating various patterns of descriptions in a short form.
For example, we use a short regular expression
\qtt{(remove|delete|erase) (data|file)}
for representing expressions like
\qsf{remove data},\qsf{erase file}, etc.

Converting a regular expression to a state transition machine is a straightforward task.
When we have a regular expression
\qtt{Find a (Chinese|Korean|Vietnamese) restaurant in (San Francisco|Chicago|New York) on Yelp.com}, 
we can parse the string and convert it into a state transition diagram
shown in Figure \ref{statemachine1}.

\begin{figure}[htb]
\includegraphics[width=90mm,bb=0 0 573 124]{figures/statemachine.pdf}
\caption{State transition diagram for finding a restaurant.}
\label{statemachine1}
\end{figure}

By traversing the nodes and links in this state machine,
we can generate the following description texts.

\begin{quote}
\small
\textsf{Find a Chinese restaurant in San Francisco} \\
\textsf{Find a Chinese restaurant in Chicago} \\
...\\
\textsf{Find a Vietnamese restaurant in New York}\\
\end{quote}

\subsubsection{Phase 2: Generating texts from a state transition diagram}

Using the state transition diagram shown in Figure \ref{statemachine1},
{\EH} generates all the strings represented in the regular expressions,
and filter them by the pattern provided by the user.

We can generate texts from a state transition diagram by traversing nodes one by one.
Starting at the start node
(\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}})
in Figure \ref{statemachine1},
we can visit other nodes via edges and generate a tree of generated texts
shown in Figure \ref{gentree1}.
After visiting the initial node
\raisebox{-2pt}{\includegraphics[height=10pt,bb=0 0 40 40]{figures/startnode.pdf}},
the system generates a string \qsf{Find a} and proceeds to the next node.
In the second generation,
the system can add \qsf{Chinese}, \qsf{Korean}, and \qsf{Vietnamese}
to \qsf{Find a}, generating
\qsf{Find a Chinese}, \qsf{Find a Korean}, etc.
The system can repeat finding edges from previously visited nodes,
and eventually generates all the strings described above.
Of course, it is impossible to generate all the strings
from a regular expression like ``\tt{(0|1)+}'' which represents infinite length of
strings consisting of \tt{0}s and \tt{1}s, so the generation should be
terminated at certain generation.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 643 398]{figures/gentree1.pdf}
\caption{Generating a text tree from a state transition machine.}
\label{gentree1}
\end{figure}

\subsection{Generate-and-Filter}

Generating all the texts in this way before finding matched strings is
inefficient, because the amount of generated texts can easily become huge.
Instead, the system performs the patter matching as soon as a text is generated,
for saving time and memory.

``Generate-and-test\footnote{
  {\sf http:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Generate\_and\_test}
}''
technique is a simple and effective strategy
used for solving puzzles and AI problems.
For example,
the ``8-Queen'' problem can be solved simply by
generating all the possible queen layouts and checking if
two or more queens are laid out on the same row, column, or diagonal line.
Although this strategy is simple, the cost of
generating all the possible solutions is prohibitive, since
the solution space of the 8-Queen puzzle is $8^8 = 16,777,216$,
which is not a small amount even for today's computers.

To solve this problem,
controlling the generation part from the testing part is effective.
In the 8-Queen problem,
whenever the testing part finds two queens in the same row or column,
it can tell the generation part to
give up current layout in the early stage and proceed to the next layout.

Similarly in our case,
it is not efficient to perform the matching operation
after generating all the texts from the regular expression,
and it is better to calculate the matching
at the time of generating each text.
We call it the \qit{generate-and-filter} strategy,
and implemented the algorithm in {\EH}.
Unlike simple puzzle problems where
conditions are strict and finding one solution is enough,
our goal is to find help description strings
that fits the query pattern while allowing errors.
For this goal,
the system should perform approximate pattern matching
without sacrificing processing speed.
%
We could implement flexible generate-and-filter by using a simple and efficient
approximate pattern matching algorithm based on the ``shifter algorithm''.

\subsection{Approximate pattern matching by shifter algorithm}

簡潔に書けるか?

@@

The data used in {\GH} are represented as {\SB} documents.
%
{\SB} is a general-purpose flexible Wiki system for
any kind of data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors, and simple
markup symbols can be used just like MarkDown\footnote{markdown}
and other markup languages.

For {\GH}, database entries like the following

% \begin{figure}[htb]
% \begin{verbatim}
% \end{verbatim}
% \centerline{\includegraphics[width=40mm]{figures/xxxxx}}
% \caption{ssss}
% \label{xxxxx}
% \end{figure}

This page describes the usage of \qtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the description of the command.
%
% Specs and command lines are specified with a special symbol, and
% all other documents can be written just like standard manuals and help documents.

Although usage examples are often shown on Unix man pages,
they cannot be used as the database of online help system.
On the other hand,
a {\SB} document contains both the manual page and the help database
at the same place.
%
This strategy is similar to the
``Literate Programming'' style,
where source codes and documents are put in the same document.

Also, since the database is on the Wiki page, any member of the
Wiki can correct the document or add additional {\GH} specifications.
When a user could not get a good support from {\GH}, he can add
{\EH} specifications to the {\SB} document himself
so that he and other people can get an appropriate support next time.

@@

On text editors an│shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \qtt{la} on the Unix shell,
\qtt{latex}, \qtt{latex}, and other commands are shown as candidates.
When a user types \qtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \tt{README.md} file, and
replace the user's input with \qtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been adopted in text editors and command line editors.

@@

Gitsome(https://github.com/donnemartin/gitsome)
helps \tt{git} users by dynamically
showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Git some is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...
